A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments

### 2014-07-10 src/paper.tex
Adjusts in cloud-computing paragraph

The TV domain has the potential of facing very different audience ratings and the amount of viewers using a particular iTV service can drastically change during the day. So, an important requirement for shared iTV services is to dynamically scale up and down the service according to workload demands. Researchers have proposed novel ideas based on cloud-computing environments to tackle this requirement~\cite{Lee2010,Lai2011}. Since the architecture presented this paper is intended for a potentially large amount of viewers, the use of a cloud-computing infrastructure is considered to handle the requests from client applications.

>>>>

The TV domain has the potential of facing very different audience ratings. As a result, the amount of viewers using a particular iTV service can drastically change during the day. So, an important requirement for shared iTV services is to dynamically scale up and down the computing resources according to workload demands. Researchers have proposed novel ideas based on cloud-computing environments to tackle this requirement~\cite{Lee2010,Lai2011}. Since the architecture presented in this paper is intended to support a potentially large amount of viewers, the use of a cloud-computing infrastructure is considered in order to handle the requests from client applications.
